The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2019-06-16 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
Added/responded to some comments in the paper .tex file

We now describe the options available for the function \texttt{nu}.
As pointed out in the introduction, if $f \in \mathfrak{m}$, the values $\nu^{\mathfrak{m}}_f(p^e)$ can be recovered from the $F$-pure threshold of $f$.
This is used to speed up computations for certain polynomials whose $F$-pure thresholds can be computed quickly via specialized algorithms, namely diagonal polynomials, binomials, and forms in two variables (see Section \ref{sec.FPT}).  This feature can be disabled by setting the option \texttt{UseSpecialAlgorithms} (default value \texttt{true}) to \texttt{false}.  Consider the following example, where $f$ is a diagonal polynomial.
\todo{Explain why the user might want to disable this.}
\bigskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i13 : R = ZZ/17[x,y,z];

@@

>>>>

We now describe the options available for the function \texttt{nu}.
As pointed out in the introduction, if $f \in \mathfrak{m}$, the values $\nu^{\mathfrak{m}}_f(p^e)$ can be recovered from the $F$-pure threshold of $f$.
This is used to speed up computations for certain polynomials whose $F$-pure thresholds can be computed quickly via specialized algorithms, namely diagonal polynomials, binomials, and forms in two variables (see Section \ref{sec.FPT}).  This feature can be disabled by setting the option \texttt{UseSpecialAlgorithms} (default value \texttt{true}) to \texttt{false}.  Consider the following example, where $f$ is a diagonal polynomial.
\todo{Explain why the user might want to disable this.}
\daniel{Why would one want to do this?}

\bigskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i13 : R = ZZ/17[x,y,z];

@@

\daniel[inline]{I like the explanation provided by activating Verbose, and so I kind of think that it would be cool to show this off.  However, I also understand if others want to omit it, and I wouldn't object if anyone has a strong preference.}

\daniel[inline]{Should the line 
\begin{center}
ν has been computed: ν = ν(3,f) = 17 ...
\end{center}
instead be
\begin{center}
ν has been computed: ν = nu(3,f) = 17 ...
\end{center}
on the 5th line of the Verbose output?  I think this would be consistent with the paper, but whoever wrote this might have had a specific reason for doing it this way.
}
